Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-06 paper/snakemajoranas.tex
edit conclusions

\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry.}
Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and Zeeman field $E_Z$.
We also observe additional gap closings which are due to the BDI symmetry that is present.
As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
Additionally, we see a cleaner and more stable topological region due to the absence of the gap closings resulting from the former mentioned chiral symmetry.

@@

\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length, now experimental verification necessary}
The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length.
Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner topological region.

\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated.
Slight modifications to the geometry, for example, to ease measurement, should not have significant implications on the physics.

\comment{It is interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake-like, and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
A study optimizing the geometry for supporting Majoranas would be an exciting continuation.

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
We exclude several physical effects, such as disorder, electrostatics, the orbital effect, etc..
Further study, as well as experimental verification, are required to see whether the conclusions of this model are valid for the real case.

>>>>

\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry.}
Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and Zeeman field $E_Z$.
We also observe additional gap closings which are due to the BDI symmetry that is present.
As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
Additionally, we see a cleaner and more stable topological region due to the absence of the gap closings resulting from the aforementioned chiral symmetry.

@@

\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing Majorana length.}
The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length, which enables experimentalists to create significantly shorter devices.
Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner and more stable topological region.

\comment{Current fabrication techniques are compatible with the proposed geometry, and experimental verification can be near.}
Current fabrication techniques are compatible with the proposed geometry; zigzag devices have already been fabricated. % XXX: add ref to Fokko's thesis
Slight modifications to the geometry, for example, to ease measurement, should not have significant implications on the physics.

\comment{It is interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth and snake-like geometries of the semiconductor region, but perhaps a more exotic shape will be optimal.
A study optimizing the geometry's parameters for supporting Majoranas is an exciting continuation of our research.

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
Finally, we exclude several physical effects, such as disorder, electrostatics, the orbital effect, the finite thickness of the sample, and electron-electron interactions, however, we expect these to be second or higher order effects which will not alter our conclusions.
